### 2008-12-11 doc/sec/SecurityFrameworkofARC1.tex
Put the added functionality into Sec technical documentation

@@

\includegraphics[width=0in,height=0.0161in]{SecurityFrameworkofARC1-img3.png}

\includegraphics[width=0in,height=0.0161in]{SecurityFrameworkofARC1-img4.png}

\includegraphics[width=0in,height=0.0161in]{SecurityFrameworkofARC1-img5.png}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ are supposed to be used to load object; element
{\textless}PolicyStore/{\textgreater} is}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ supposed to be used to get the location of
policy-{}-{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ {\textless}pdp:PDPConfig{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}pdp:PolicyStore{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ {\textless}Location
Type={\textquotedbl}file{\textquotedbl}{\textgreater}Policy\_Example.xml{\textless}/Location{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ {\textless}!-{}- other policy
location-{}-{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}/pdp:PolicyStore{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}pdp:Evaluator
name={\textquotedbl}arc.evaluator{\textquotedbl} /{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}pdp:Policy
name={\textquotedbl}arc.policy{\textquotedbl} /{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}pdp:Request
name={\textquotedbl}arc.request{\textquotedbl} /{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ {\textless}/pdp:PDPConfig{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ {\textless}PDP
name={\textquotedbl}arc.pdp{\textquotedbl}{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ {\textless}PolicyStore{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ {\textless}Location
type={\textquotedbl}file{\textquotedbl}{\textgreater}Policy\_Example.xml{\textless}/Location{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ {\textless}!-{}-other policy
location-{}-{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ {\textless}/PolicyStore{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ {\textless}/PDP{\textgreater}}}

@@

\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ {\textless}Rule
Effect={\textquotedbl}Permit{\textquotedbl}{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ {\textless}Description{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ Example policy for echo service}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ {\textless}/Description{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}Subjects{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Subject{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ {\textless}Attribute

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}/C=NO/ST=Oslo/O=UiO/CN=CA{\textless}/Attribute{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ {\textless}Attribute

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}/C=NO/ST=Oslo/O=UiO/CN=test{\textless}/Attribute{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}/Subject{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}/Subjects{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}Resources{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Resource

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}/Echo{\textless}/Resource{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}/Resources{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}Actions{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Action

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}POST{\textless}/Action{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Action

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}GET{\textless}/Action{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Action

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}echo{\textless}/Action{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}/Actions{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}Conditions/{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ {\textless}/Rule{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ {\textless}!-{}-Remote pdp service
invoking-{}-{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ {\textless}PDP
name={\textquotedbl}pdpservice.invoker{\textquotedbl}{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ {\textless}ServiceEndpoint{\textgreater}https://127.0.0.1:60001/pdp.service{\textless}/ServiceEndpoint{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ {\textless}KeyPath{\textgreater}./key.pem{\textless}/KeyPath{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ {\textless}CertificatePath{\textgreater}./cert.pem{\textless}/CertificatePath{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ {\textless}CACertificatePath{\textgreater}./ca.pem{\textless}/CACertificatePath{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ {\textless}/PDP{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ {\textless}PDP
name={\textquotedbl}delegation.pdp{\textquotedbl}/{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ {\textless}/SecHandler{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ {\textless}next
id={\textquotedbl}echo{\textquotedbl}/{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}tls.service{\textquotedbl}
id={\textquotedbl}tls{\textquotedbl}{\textgreater} {\textless}next
id={\textquotedbl}http{\textquotedbl}/{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:KeyPath{\textgreater}./key.pem{\textless}/tls:KeyPath{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:CertificatePath{\textgreater}./cert.pem{\textless}/tls:CertificatePath{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:CACertificatePath{\textgreater}./ca.pem{\textless}/tls:CACertificatePath{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ {\textless}!-{}-delegation.collector
must be inside tls MCC-{}-{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}/Component{\textgreater}}}

@@

\subsubsection[UsernameToken SecHandler configuration]{UsernameToken
SecHandler configuration}
{\selectlanguage{english}\upshape\color{black}
Configuration XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTokenSH.xsd}
.}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}soap.service{\textquotedbl}
id={\textquotedbl}soap{\textquotedbl}{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}echo{\textquotedbl}/{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ {\textless}SecHandler
name={\textquotedbl}usernametoken.handler{\textquotedbl}
id={\textquotedbl}usernametoken{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}Process{\textgreater}extract{\textless}/Process{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}PasswordSource{\textgreater}password.txt{\textless}/PasswordSource{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ {\textless}/SecHandler{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}/Component{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}soap.service{\textquotedbl}
id={\textquotedbl}soap{\textquotedbl}{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}echo{\textquotedbl}/{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ {\textless}SecHandler
name={\textquotedbl}x509token.handler{\textquotedbl}
id={\textquotedbl}x509token{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}Process{\textgreater}extract{\textless}/Process{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}CACertificatePath{\textgreater}ca.pem{\textless}/CACertificatePath{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ \ \ {\textless}/SecHandler{\textgreater}}}

@@

{\selectlanguage{english}\upshape\color{black}
\texttt{\ \ \ \ \ \ \ {\textless}/Component{\textgreater}}}

{\selectlanguage{english}\upshape\color{black}
X509Token SecHandler must be configured under SOAP MCC.}

>>>>

\newcommand\liststyleLi{%

@@

\includegraphics[width=0.0161in,height=0.0161in]{SecurityFrameworkofARC1-img3.png}

\includegraphics[width=0.0161in,height=0.0161in]{SecurityFrameworkofARC1-img4.png}

\includegraphics[width=0.0161in,height=0.0161in]{SecurityFrameworkofARC1-img5.png}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ are supposed to be used to load object; element
{\textless}PolicyStore/{\textgreater} is}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ supposed to be used to get the location of
policy-{}-{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ {\textless}pdp:PDPConfig{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}pdp:PolicyStore{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ {\textless}Location
Type={\textquotedbl}file{\textquotedbl}{\textgreater}Policy\_Example.xml{\textless}/Location{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ {\textless}!-{}- other policy
location-{}-{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}/pdp:PolicyStore{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}pdp:Evaluator
name={\textquotedbl}arc.evaluator{\textquotedbl} /{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}pdp:Policy
name={\textquotedbl}arc.policy{\textquotedbl} /{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}pdp:Request
name={\textquotedbl}arc.request{\textquotedbl} /{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ {\textless}/pdp:PDPConfig{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}PDP
name={\textquotedbl}arc.pdp{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ {\textless}PolicyStore{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Location
type={\textquotedbl}file{\textquotedbl}{\textgreater}Policy\_Example.xml{\textless}/Location{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}!-{}-other policy location-{}-{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ {\textless}/PolicyStore{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}/PDP{\textgreater}}

@@

\ \ \ {\textless}Rule
Effect={\textquotedbl}Permit{\textquotedbl}{\textgreater}}
\ \ \ \ \ {\textless}Description{\textgreater}}
\ \ \ \ \ \ \ Example policy for echo service}
\ \ \ \ \ {\textless}/Description{\textgreater}}
\ \ \ \ \ \ {\textless}Subjects{\textgreater}}
\ \ \ \ \ \ \ \ \ {\textless}Subject{\textgreater}}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}Attribute

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}/C=NO/ST=Oslo/O=UiO/CN=CA{\textless}/Attribute{\textgreater}}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}Attribute

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}/C=NO/ST=Oslo/O=UiO/CN=test{\textless}/Attribute{\textgreater}}
\ \ \ \ \ \ \ \ \ {\textless}/Subject{\textgreater}}
\ \ \ \ \ \ {\textless}/Subjects{\textgreater}}
\ \ \ \ \ \ {\textless}Resources{\textgreater}}
\ \ \ \ \ \ \ \ \ {\textless}Resource

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}/Echo{\textless}/Resource{\textgreater}}
\ \ \ \ \ \ {\textless}/Resources{\textgreater}}
\ \ \ \ \ \ {\textless}Actions{\textgreater}}
\ \ \ \ \ \ \ \ \ {\textless}Action

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}POST{\textless}/Action{\textgreater}}
\ \ \ \ \ \ \ \ \ {\textless}Action

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}GET{\textless}/Action{\textgreater}}
\ \ \ \ \ \ \ \ \ {\textless}Action

@@

Type={\textquotedbl}string{\textquotedbl}{\textgreater}echo{\textless}/Action{\textgreater}}
\ \ \ \ \ \ {\textless}/Actions{\textgreater}}
\ \ \ \ \ \ {\textless}Conditions/{\textgreater}}
\ \ \ {\textless}/Rule{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}!-{}-Remote pdp service invoking-{}-{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ {\textless}PDP
name={\textquotedbl}pdpservice.invoker{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}ServiceEndpoint{\textgreater}https://127.0.0.1:60001/pdp.service{\textless}/ServiceEndpoint{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}KeyPath{\textgreater}./key.pem{\textless}/KeyPath{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}CertificatePath{\textgreater}./cert.pem{\textless}/CertificatePath{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}CACertificatePath{\textgreater}./ca.pem{\textless}/CACertificatePath{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ {\textless}/PDP{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}PDP
name={\textquotedbl}delegation.pdp{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ {\textless}/SecHandler{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ {\textless}next
id={\textquotedbl}echo{\textquotedbl}/{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}tls.service{\textquotedbl}
id={\textquotedbl}tls{\textquotedbl}{\textgreater} {\textless}next
id={\textquotedbl}http{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:KeyPath{\textgreater}./key.pem{\textless}/tls:KeyPath{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:CertificatePath{\textgreater}./cert.pem{\textless}/tls:CertificatePath{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:CACertificatePath{\textgreater}./ca.pem{\textless}/tls:CACertificatePath{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}!-{}-delegation.collector must be
inside tls MCC-{}-{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ {\textless}/Component{\textgreater}}

@@

\subsection[Web Service Security Support]{\color{black} Web Service
Security Support}
\subsubsection[UsernameToken SecHandler configuration]{UsernameToken
SecHandler configuration}
{\selectlanguage{english}\upshape\color{black}
Configuration XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTokenSH.xsd}
.}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}soap.service{\textquotedbl}
id={\textquotedbl}soap{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}echo{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ {\textless}SecHandler
name={\textquotedbl}usernametoken.handler{\textquotedbl}
id={\textquotedbl}usernametoken{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}Process{\textgreater}extract{\textless}/Process{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}PasswordSource{\textgreater}password.txt{\textless}/PasswordSource{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ {\textless}/SecHandler{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}/Component{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}soap.service{\textquotedbl}
id={\textquotedbl}soap{\textquotedbl}{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}echo{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}SecHandler
name={\textquotedbl}x509token.handler{\textquotedbl}
id={\textquotedbl}x509token{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}Process{\textgreater}extract{\textless}/Process{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}CACertificatePath{\textgreater}ca.pem{\textless}/CACertificatePath{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}/SecHandler{\textgreater}}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ {\textless}/Component{\textgreater}}

{\selectlanguage{english}\color{black}
X509Token SecHandler must be configured under SOAP MCC.}

\subsection[Using Shibboleth IdP for Authentication and Attribute-based
Authorization]{Using \foreignlanguage{english}{Shibboleth} IdP for
Authentication and Attribute-based Authorization}
{\selectlanguage{english}\color{black}
\ \ \ \ In grid community, GSI (grid security infrastructure) is the
de-facto standard about transport level communication for the legacy
grid solution, which implements some enhancement (such as delegation)
based on standard SSL3.0/TLS1.0. In ARC1, besides that GSI is supported
for talking with external grid services which are based on GSI, the
standard TLS/SSL is also supported.}

{\selectlanguage{english}\color{black}
\ \ \ \ No matter standard SSL/TLS or GSI is used, SSL/TLS based mutual
authentication applies for both of them, and is the default
configuration for grid deployment; and X.509 certificate is required
for both of the client and service sides. X.509 certificates is issued
by certificate authorities (CA), and then CAs constitute trust
federation and guarantee two different X.509 certificates from
different CAs can accomplish authentication to each other. So if a user
would access grid system, he/she should own a X.509 certificate which
is issued by a CA that is trusted by other{\textquotesingle}s entity in
the grid system.}

{\selectlanguage{english}\upshape\color{black}
\ AAI (Authentication and Authorization Infrastructure) is a solution
for the authentication and authorization in inter-organization resource
sharing, such as electronic resource sharing between libraries, etc.
AAI implicitly applies to community or institutional based
authentication where users from different home communities need to get
resources from other communities by using some federation mechanism.
Unlike the X.509 based authentication solution in current Grid systems,
AAI does not require users to provide X.509 certificate, instead, it
can support different types of authentication, such as
username/password authentication, IP address authentication, etc. There
are several implementations of AAI, among which Shibboleth is one
implementation which has been widely deployed.}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ Shibboleth provides cross-domain single sign-on and
attribute-based authorization while preserving user privacy. It is
based on the OASIS Security Assertion Markup Language (SAML),
specifically, the new version of Shibboleth supports SAML 2.0
specification. For authentication, the main SAML profile that
Shibboleth implements is the SAML2.0 web browser SSO profile, which
defines two functional components, an Identity Provider and a Service
Provider. The Identity Provider (IdP) is responsible for creating,
maintaining, and managing user identity, while the Service Provider
(SP) is responsible for controlling access to services and resources by
using the SAML assertion produced and issued by IdP upon request. In
order to discover which home community does a user come from,
Shibboleth specifies an optional third component called
{\textquotedblleft}Where Are You From?{\textquotedblright} (WAYF)
service to \ aid in the process of IdP discovery, and this IdP
discovery process is also standardized and defined in SAML 2.0
specification and called as {\textquotedblleft}Identity Profile
Discovery Profile{\textquotedblright}.}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ The SAML2.0 web browser SSO profile is utilized for the
authentication in ARC middleware. But since the SSO profile is
primarily supposed to protect Web applications and provide
authentication for Web users, some external code on the client and
service side is implemented to integrate the SSO profile. On the client
side, apart from the client interface for writing Web Service client,
the user agent functionality of the Web browser is implemented in order
to mimic its behavior, such as HTTP redirection and cookie processing.
In fact, implementation of the user agent is also based on the client
interface of ARC, specifically, the HTTPs client interface, since the
client interface of ARC can support different protocols which are
incarnated by different MCCs. The client developers who would use
SAML2.0 SSO profile should call the user agent interface and then the
Web Service client interface. On the service side, the Service Provider
functionality (based on the HTTP MCC configured together with TLS MCC)
is implemented, which is called SP Service. For Identity Provider, the
Shibboleth IdP implementation is used. Figure 6 shows the process of
SAML2.0 SSO integrated in ARC client and service.}

\begin{center}
\includegraphics[width=3.2256in,height=1.8472in]{SecurityFrameworkofARC1-img7.png}
\end{center}

{\centering\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}.\textbf{ }SAML2.0 SSO profile in
ARC
\par}

{\selectlanguage{english}\color{black}
\ The steps shows in Figure 6 are described as follows:}

\liststyleLi
\begin{enumerate}
\item {\selectlanguage{english}\color{black}
The client uses the user agent interface to launch a HTTP request
including the IdP name (to which the user belongs) to the service side.
The endpoint of the SP (Service Provider) service is the same as that
of the other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that the user who would
access the target services should better know where is he from
initially.}
\item {\selectlanguage{english}\color{black}
The SP Service searches the metadata (we use the same metadata format as
defined in Shibboleth) and gets the location of the single sign-on
service (hosted in IdP) and also the location of assertion consuming
service (hosted in this SP itself) in order to compose the SAML
{\textless}samlp:AuthnRequest{\textgreater} message. Then SP Service
issues this {\textless}samlp:AuthnRequest{\textgreater} message by
using its own X.509 certificate (note that in the SAML SSO profile,
X.509 certificates are still needed for IdP and SP) and sends back to
user agent.}
\item {\selectlanguage{english}\color{black}
User agent sends the {\textless}samlp:AuthnRequest{\textgreater} message
to the Identity Provider.}
\item {\selectlanguage{english}\color{black}
Identity Provider requires an act of authentication. The authentication
mechanism is outside of the SAML2.0 SSO profile. Shibboleth IdP
implementation chooses some login handlers for authentication. The
current user agent implementation is compatible with the
Username/Password login handler of Shibboleth IdP. Through the HTTP
protocol, the user agent will feed IdP with the username/password which
has been given by the caller of user agent interface.}
\item {\selectlanguage{english}\color{black}
Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquoteright}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider.}
\item {\selectlanguage{english}\color{black}
The SP Service verifies and checks the SAML response, decrypts and
stores the SAML assertion into session/connection context. The SAML
assertion includes the {\textless}saml:AuthnStatement{\textgreater} and
{\textless}saml:AttributeStatement{\textgreater}.}
\item {\selectlanguage{english}\color{black}
The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.}
\item {\selectlanguage{english}\color{black}
The Grid/Web Service checks the
{\textless}saml:AuthnStatement{\textgreater} from the session context
to see if the session is still valid through the SecHandler called
{\textquotedblleft}SAML SecHandler{\textquotedblright}. If valid,
service handles the service processing and returns the response to WS
client. Note that service requires that WS client is from the same
connection as the one on which user agent contact SP service, in order
to guarantee that the validity of SSO profile result effects the WS
client/Web Service interaction.}
\end{enumerate}
{\selectlanguage{english}\upshape\color{black}
\ \ \ \ The SP service and other functional service(s) are hosted by the
same container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquoteright}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for the client
side, so that SP and IdP can authenticate themselves to the client. As
required by the SAML2.0 profile, the SP and IdP should have trust
relationship to each other.}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ One benefit of the SAML2.0 SSO profile that is worth mentioning
is: the Identity Provider could cache the authentication result through
session management once the user agent has succeeded to authenticate;
then for a short period this authentication result is valid so that the
user agent doesn{\textquoteright}t need to feed IdP with
user{\textquoteright}s username and password the next time (if this
point of time is not out of the scope of valid period) it authenticates
against IdP. So user (or the client on behalf of this user) can travel
across multiple security \ domains with only providing his name and
password once, which is the characteristic of single sign-on.}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ Since the Shibboleth implementation of SAML is
standard-compliant and widely deployed, the solution implemented in ARC
can easily interoperate with other SAML implementations with minimum
change, and more importantly, this solution can succeed to utilize the
widely deployed SAML implementation for authentication in Grid systems
by avoiding the usage of X.509 certificate.}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ Moreover, even though the implementation is based on the ARC
middleware, the idea can be adopted by other Grid middlewares if they
only require server authentication instead of mutual authentication.}

\subsection[\ Short-Lived Credential
Service]{\foreignlanguage{english}{\ }Short-Lived Credential Service}
{\selectlanguage{english}\color{black}
\ \ \ \ However, most of the widely used Grid middlewares are based on
GSI while GSI requires mutual authentication. Also for Web Service
based Grid solution, we cannot prevent service side from requiring
client X.509 certificate. Based on the solution described in Section 9,
a short lived credential service (SLCS) is implemented by which user
can get a short-lived X.509 certificate without being bothered to
contact any registration authority (RA) or certificate authority (CA).}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ The SLCS service is also a Web Service (standard Web Service
implemented by using ARC service interface), and the SLCS client is a
specific command-line interface (CLI) which includes the user agent and
WS client. The whole process of SLCS invocation is showed in Figure 7
(from step 1 to step 8), which is the same as in Figure 6, except that
step 7 and step 8 are invoked for the SLCS certificate request and
response.}

\begin{center}
\includegraphics[width=3.7689in,height=3.2055in]{SecurityFrameworkofARC1-img8.png}
\end{center}
{\centering\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}.Short lived credential service
\par}
